% Introduction 
\section{Introduction}
\subsection{Relational Databases}
\begin{frame}{Relational Databases}
    Relational databases are those based on \emph{Relational Model}, invented by \emph{E.F. Codd}.
    
    The relational model define that all the data is represented in terms of \alert{tuples}, grouped in \alert{relations}. These relations consists of a set of attributes and a set of $n$ tuples, and are called \alert{tables}.
\end{frame}
\begin{frame}{Relational Databases: Pros vs Cons}
    \begin{columns}[t]
        \begin{column}{.5\textwidth}
            \begin{exampleblock}{\huge\faThumbsOUp}
                \begin{itemize}
                    \item Structured data
                    \item Strong typing
                    \item Integrity and constraints
                    \item Indexes
                    \item Support
                    \item Fast querying
                    \item Maturity
                \end{itemize}
            \end{exampleblock}
        \end{column}
        \begin{column}{.5\textwidth}
            \begin{alertblock}{\huge\faThumbsODown}
                \begin{itemize}
                    \item Admin
                    \item Poor horizontal scaling
                    \item Schema and data migrations
                \end{itemize}
            \end{alertblock}
        \end{column}
    \end{columns}
\end{frame}

\subsection{NoSQL Databases}
\begin{frame}{NoSQL Databases}
    \begin{block}{Key-Value}
        Key-Value stores are the simplest NoSQL data stores. The value is a blob, and due to primary-key access they have a great performance and scalability.
    \end{block}
    \begin{block}{Document}
        Documents are the main concept in document databases. The database stores and retrieves documents, which can be XML, JSON, BSON, and so on.
    \end{block}
    \begin{block}{Column family}
        Column-family databases store data in column families as rows that have many columns associated with a row key.
    \end{block}
    \begin{block}{Graph}
        Graph databases allow you to store entities and relationships between these entities. Entities are also known as nodes, which have properties. Relations are known as edges that can have properties. 
    \end{block}
    
    \note {
        Memcached and Redis as \textbf{Key-Value} databases.
        
        MongoDB as \textbf{document} database.

        Cassandra is a \textbf{column family} database. These databases are like relational tables but each row can have a different subset of columns.
        
    In \textbf{graph} databases think of a node as an instance of an object in the application. OrientDB and Neo4j.
    }
\end{frame}
\begin{frame}{NoSQL Databases: Pros vs Cons}
    \begin{columns}[t]
        \begin{column}{.5\textwidth}
            \begin{exampleblock}{\huge\faThumbsOUp}
                \begin{itemize}
                    \item Fast writing
                    \item Horizontal scaling
                    \item Reduced admin tasks
                    \item Flexible
                    \item Mostly open-source
                \end{itemize}
            \end{exampleblock}
        \end{column}
        \begin{column}{.5\textwidth}
            \begin{alertblock}{\huge\faThumbsODown}
                \begin{itemize}
                    \item Slow querying
                    \item Support
                    \item Maturity
                \end{itemize}
            \end{alertblock}
        \end{column}
    \end{columns}
\end{frame}

\subsection{Relational vs NoSQL}
\begin{frame}[standout]
    \huge{Should I use a Relational or NoSQL database?}

    \huge{\faDatabase}
\end{frame}
